\documentclass[11pt, a4paper, sans]{moderncv}
\moderncvstyle{fancy} % Style options: 'casual' (default), 'classic', 'banking', 'oldstyle', 'fancy'
\moderncvcolor{black} % Color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', 'black'

\usepackage[scale=0.85]{geometry} % Adjust margin sizes
\setlength{\hintscolumnwidth}{4cm} % Increase the width of the dates column if needed

\name{Adele M.}{Hedrick, M.Sc}
\address{Cobourg, Ontario}
\phone[mobile]{+1 905-449-8435}
\email{adele@hedrick.ca}

\begin{document}
\makecvtitle

\section{Skills}
\cvitem{Programming Languages}{Python (Pandas \& PySpark), Golang, PHP, Node.js, Clojurescript, Angular}
\cvitem{Cloud Platforms}{AWS, GCP}
\cvitem{DevOps}{GitActions, Jenkins, Terraform, Docker, Datadog, Automated Unit Tests}
\cvitem{Data Engineering}{Apache Airflow, DBT, Pentaho, AWS Services (Step Functions, Glue, Lambda, Athena, SQS, SNS) GCP Services (Dataproc), Thingsboard}
\cvitem{Relational Databases}{DB2, SQLServer, PostgreSQL, Redshift, MySQL, SQLite, MariaDB, Google BigQuery}
\cvitem{Visualization}{D3, Plotly, Qlik}
\cvitem{Data Modeling}{Data Warehouse, Data Mart, OLTP, OLAP, Data Lake}
\cvitem{Machine Learning}{XGBoost, Forecasting, LLM, Prompt Engineering, Chat GPT}



\section{Experience}
\subsection{360insights}
\cventry{Jan 2021 -- Present}{Head Data Science}{Whitby, ON}{}{}{}
\cventry{Nov 2020 -- Jul 2021}{Team Lead, Data Science}{}{}{}{}
\cventry{Jul 2020 -- Nov 2020}{Data Science \& Engineering Consultant}{}{}{}{}
\cventry{Jul 2018 -- Nov 2019}{Data Scientist}{}{}{}{}
\cventry{Jul 2017 -- Jul 2018}{Software Developer}{}{}{}{
    \begin{itemize}
        \item Supported team members in creating custom integrations to send and receive data to/from Reltio, a Master Data Management Software.
        \item Collaborated with Reltio Professional services to get our first set of domain entities and relationships modelled and populated with data in Reltio.
        \item Elected to be one of 6 Culture Ambassadors for 2018/2019 at the Whitby headquarters, dedicated to promoting a positive culture in the workplace and community.
        \item Awarded for facilitating a positive team culture providing psychological safety resulting in more innovation and a high performing team.
        \item Designed the Operational Data Store (OLTP) and kept alignment with the Analytic Data Store (OLAP) that was being designed by a colleague.
        \item Enabled actionable insights for multiple clients with rapidly developed Qlik dashboards.
        \item Generated ad-hoc reports, extracting data from multiple sources and formats, to investigate system behaviour, diagnose problems, and generate import files to correct data discrepancies.
        \item Built a generic data pipeline that would clean, conduct feature selection, parameter tuning, train an XGBoost model, predict and analyse results.
        \item Developed use case specific connector to extract data and generate over 300 features.
        \item Reduced manual risk analysis by 85\%, leaving 15\% of the claims to have the reviews augmented with information from the risk model to support the reviewer.
        \item Scaled the forecasting service by building a generic forecasting service on AWS, capable of generating hundreds of forecasts in parallel, reducing the time to generate these reports from +24 hours to less than 15 minutes.
        \item Developed a versatile utility enabling users to define data connections and analytics requirements via JSON, automating the generation of Excel spreadsheets and PowerPoint reports; includes a backend mechanism that dynamically constructs tailored star schema database tables to efficiently deliver the requested analytics.
        \item Created a CI/CD pipeline with GitActions to support the GitHub flow development workflow and deployment.
        \item Created a robust unit testing system for an AWS system that would mock out external services to support the tests being executed in an isolated continuous integration environment.
    \end{itemize}
}

\subsection{Datalogy}
\cventry{April 2024 -- Present}{Data Science \& Eng. Consultant}{Toronto, ON}{}{}{
    \begin{itemize}
        \item Developing a prototype to demonstrate AI capabilities in extracting text and context from images, specifically targeting invoice processing.
    \end{itemize}
}

\subsection{InvestDefy}
\cventry{Mar 2023 -- Jun 2023}{Data Science \& Eng. Consultant}{Toronto, ON}{}{}{
    \begin{itemize}
        \item Optimized Airflow DAGs for enhanced generality and reusability, significantly reducing development time and accelerating insight generation.
        \item  Automated feature engineering and predictive modeling for cryptocurrency price trends.
    \end{itemize}
}

\subsection{RealTech}
\cventry{Nov 2019 -- Mar 2020}{Data Scientist}{Whitby, ON}{}{}{
    \begin{itemize}
        \item Reduced turn around time of device calibration service by replacing a manual process with a pipeline that included querying an API. Supported engineering with RoHS compliance.
    \end{itemize}
}

\subsection{IBM Canada}
\cventry{Mar 2016 -- May 2017}{Software Developer}{Toronto, ON}{}{}{
    \begin{itemize}
        \item Developed backend infrastructure for a learning management system (LMS), enhancing storage and organization of educational content. Led the creation of a data analytics-driven reporting system to improve course assessments and content.
    \end{itemize}
}

\section{Certifications}
\cvitem{2024}{Data Steward Foundation Certification, Reltio}
\cvitem{2024}{Test Lead Foundation Certification, Reltio}
\cvitem{2023}{Certified SAFe 6 Practitioner, Scaled Agile, Inc.}
\cvitem{2020}{Design Thinking Applied to AI and Machine Learning Workshop, TMLS}
\cvitem{2018}{Qlik Sense Business Analyst Qualification, Qlik}
\cvitem{2018}{Qlik Sense Data Architect Qualification, Qlik}
\cvitem{2018}{TDWI Advanced Data Modeling Techniques, TDWI}

\section{Education}
\cventry{2017}{M.Sc in Computer Science}{}{Ontario Tech University}{\textit{GPA: 4.12}}{}
\cventry{2013}{B.Ed in Education}{}{Ontario Tech University}{\textit{GPA: 4.0}}{}
\cventry{2008}{B.Sc in Computer Science}{}{Ontario Tech University}{\textit{GPA: 3.54}}{}
\cventry{2003}{Adv. 3-year Diploma in Multimedia Design}{}{Durham College}{}{}{}

\section{Publications}
\cventry{2018}{Modeling Transition and Mobility Patterns}{}{}{}{Discusses the modeling of user transitions and mobility patterns without cloud services, preserving privacy.}
\cventry{2015}{Hierarchical Temporal Mobility Analysis with Semantic Labeling}{}{}{}{Focuses on deducing salient locations and mobility patterns from WiFi signals.}
\cventry{2012}{Authoring Relational Queries on the Mobile Devices}{}{}{}{Describes the design and implementation of a user interface for interacting with a relational database on mobile devices.}

\section{Projects}
\cvitem{}{\textbf{Generic Temporal Feature Generation}. Developed for Google Cloud Provider and BigQuery. Utilizes DBT and PySpark to create temporal features for data analysis.}
\cvitem{}{\textbf{Resume AI Tailor}. Developed a Python application that tailors resumes and cover letters to specific job postings, enhancing job application success. Integrated OpenAI's API to analyze job descriptions and automatically generate customized content, demonstrating advanced usage of AI technologies. Implemented web scraping with Selenium to fetch job postings dynamically and processed documents using LaTeX, showcasing skills in web automation and document manipulation.}

\end{document}
